Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-10 paper/paper.tex
wrote some paper

	\subsection{Train the Network}\label{subsec:train-the-network}
	At first, we randomly shuffled the training set and divided it into several batches.
	These batches ,instead of single pixel, would be feed into the model for training to accelerate the training process.
	In our experiment, considering the training speed and final accuracy, we set the batch size as 50.

	\section{EXPERIMENT}\label{sec:experiment}

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}

	\subsection{Environment}\label{subsec:environment}

>>>>

	\subsection{Train the Network}\label{subsec:train-the-network}
	At first, we randomly shuffled the training set and divided it into several batches.
	These batches ,instead of single pixel, would be feed into the model for training to accelerate the training process.
	In our experiment, considering the training speed and final accuracy, we set the batch size to 50.
	As for the loss function, we adopted the margin loss mentioned in section~\ref{sec:related-works}, instead of the
	usually used cross-entropy loss function.
	The network is trained using a first-order gradient-based optimization of stochastic objection, referred to as the
	Adam algorithm.
	Therefore, our training goal is to minimize the margin loss using the Adam optimizer, and we set the learning rate
	to 0.0001.
	When all batches have been fed into the network and finished training, we say the training process finished an epoch.
	In our experiment, we conducted 100 epochs for each of the dataset.

	\section{EXPERIMENT}\label{sec:experiment}
	In this section, we showed and analyzed the training result.
	We compared our model with six neural network based algorithms i.e., 1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	the CapsNet that is identical to our DCCN model except the spectral channel and the machine learning algorithm SVM\@.
	The accuracy metrics we used includes overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
	a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset.

	\subsection{Environment}\label{subsec:environment}
	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
	and 128GB of memory.
	The operating system is Ubuntu server 18.04 x64 LTS\@.
	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.
